### 2018-05-25 manuscript/visualdesign.tex
abs, intro, updated

This work we try to answer following questions:

@@

\begin{itemize}
\item \textbf{C1: semantic understanding of demographic cahracteristics}: since the concept of groups is vague to define directly quantitativily. The visual design needs to consider how to help end-users to pick desirable ones from the mass. 
\item \textbf{C2: }
\end{itemize}

@@

The key of our work is to align the analysis of urban dynamics with the available of individual characteristics.

>>>>

This work we try to answer a couple of questions:

@@

\begin{itemize}
\item \textbf{C1: semantic understanding of demographic cahracteristics}: since the concept of groups is vague to define directly quantitativily. The visual design needs to consider how to help end-users to pick desirable ones from the mass. 
\item \textbf{C2: multivariate comparison in the constraint of spatial space}: 
\end{itemize}

@@

The key of our work is to align the analysis of urban dynamics with the available of demographic characteristics.
